Inferring Invariants of Distributed Programs

### 2015-02-27 Doc/paper.tex
Edited Introduction, Moved Related work to the end

Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or network fail, this means that there are many corner cases that developers should consider when building the system. Building such a reliable and dependable system is not possible without thorough testing of the system. But unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation. There are many failure scenarios that distributed system should handle and these scenarios should be tested as well. In some cases reproducing the failures is a difficult task e.g. degrading network performance for test purposes. Many bugs turn out to be heisenbugs in distributed system which are hard to reproduce and detect. For testing and debugging distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and looking for incidents that system does not behave as expected. One alternative to this laborious approach is to define invariants for system’s expected behaviour and check the software traces against these invariants. This approach is considerably easier than the former but as the system gets larger and more complex, providing invariants manually becomes more difficult to the point that it is not feasible any more.

Our approach is to automatically infer these invariants. To this end, we execute distributed programs and dynamically select a set of variables in each node that likely represent the distributed state across our distributed nodes. We do so with dynamic data flow analysis of variables and selecting those that are affected by a send or receive operation. Finally we use Daikon to infer invariants among our distributed state variables.

@@

%2 daikon : I do not know how to describe other paper because they are basically the same
%almost-invariant
%paxos proving using dykon
\section{Approach}

@@

>>>>

Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or network fail, this means that there are many corner cases that developers should consider when building the system. Building such a reliable and dependable system is not possible without thorough testing of the system. But unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation. There are many failure scenarios that distributed system should handle and these scenarios should be tested as well. In some cases reproducing the failures is a difficult task e.g. degrading network performance for test purposes. Many bugs turn out to be heisenbugs in distributed system which are hard to reproduce and detect. For testing and debugging distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and looking for incidents that system does not behave as expected. One alternative to this laborious approach is to define invariants for system’s expected behaviour and check the software traces against these invariants. This approach is considerably easier than the former but as the system gets larger and more complex, providing invariants manually becomes more difficult.

Testing distributed systems is hard because a fault in a single node does not confine to that node, instead it may cause an error in another node. In fact errors in distributed system should be defined on global state of the system not a single node. In this work we assume that state of each node is comprised of its variables. Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state of that node. We refer to set of distributed state of all nodes as distributed state of the system.

Our approach is to automatically infer invariants that may exist in distributed state of our system. To this end, we execute distributed programs and dynamically select a set of variables in each node that likely represent the distributed state across our distributed nodes. We do so with dynamic data flow analysis of variables and selecting those that are affected by a send or receive operation. Finally we use Daikon to infer invariants among our distributed state variables.

@@

\section{Approach}

@@

%2 daikon : I do not know how to describe other paper because they are basically the same
%almost-invariant
%paxos proving using dykon
